FASTQ -> VCF workflow for WGS data

### 2021-11-05 WGS_intro.Rmd
Added WGS tutorials

---
bibliography: bibtexlib.bib
---

@@

# Whole Genome Resequencing for Population Genomics  
For the purposes of this guide, we use "whole genome (re)sequencing (WGS)) to refer to  methods where a reference genome exists (whether for the focal species or a related species), and samples are sequenced and then mapped to most or all of the reference genome. This method can provide high density SNPs, structural information...for population genomic analyses. This is separate from whole-genome de novo sequencing, which aims to produce a reference genome by sequencing and assembling a complete genome for the first time.   
WGS can be divided into three main approaches, and choosing between these or RADseq(link to ) mostly depends on your questions of interest.   
1) high coverage individual WGS (hcWGS)  
+ description  
2) low coverage individual WGS (lcWGS)  
+ description
3) pooled individuals (Poolseq)  
RADseq is... and m

 also a factor of your funds and how you choose to allocate them. There is a financial trade-off between the number of samples you can genotype individually and the amount of sequencing coverage per sample. If you have 1000s of samples, it may not be financially feasible to sequence most of them to high depth.  Large genome sizes can also make hcWGS cost-prohibited. This topic was discussed during the MarineOmics WGS panel seminar (link).    
An excellent and thorough review of the pros  between these approaches, esp. as they apply to nonmodel organisms, is [Fuentes-Pardo and Ruzzante 2017)(link).

@@

* Fastq-to-VCF pipeline(link): In-depth explanation of automated short-read mapping and variant calling pipeline maintained by [Harvard Informatics](https://github.com/harvardinformatics/shortRead_mapping_variantCalling). Useful for moderate to high coverage data, where *add description of why one would use pipeline*  
*

# Considerations Before Lab Work

>>>>

---
bibliography: RCN_site-Nov05.bib
---

@@

# Whole Genome Resequencing for Population Genomics  
For the purposes of this guide, we use "whole genome (re)sequencing (WGS)) to refer to  methods where a reference genome exists (whether for the focal species or a related species), and samples are sequenced and then mapped to most or all of the reference genome. This method can provide high density SNPs, structural information...for population genomic analyses. This is separate from whole-genome de novo sequencing, which aims to produce a reference genome by sequencing and assembling a complete genome for the first time.

An excellent and thorough review of the pros  between these approaches, esp. as they apply to nonmodel organisms, is [@Fuentes-Pardo2017-nu].

@@

* [Fastq-to-VCF SnakeMate pipeline](fastq2vcf_pipeline.html): In-depth explanation of automated short-read mapping and variant calling pipeline maintained by [Harvard Informatics](https://github.com/harvardinformatics/shortRead_mapping_variantCalling). Useful for moderate to high coverage data, where *add description of why one would use pipeline*  
* [Fastq-to-VCF workflow](WGS-Full-Walkthrough.html): detailed walkthrough of processing 15x sequencing depth WGS data for cod, from raw reads to a VCF.

# References
